### 2019-04-24 sections/introduction.tex
convert back to two column layout
rename main tex file to main
micro-optimise sentence in introduction

\subsection{Tasks}

@@

\subsection{Task-oriented programming}
\label{sec:top}

@@

% Task-Oriented Programming (\TOP) is a programming paradigm aimed at writing interactive multi-user applications in a declarative way \cite{conf/ppdp/PlasmeijerLMAK12}.
Task-oriented programming (\TOP) is a programming paradigm which targets the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting these workflows \cite{conf/ppdp/PlasmeijerLMAK12}.
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
\TOP focusses on modelling collaboration patterns.
This gives rise to a user's need to interact and share information.
Next to that, \TOP automatically provides solutions to common development jobs like designing \GUI{s}, connecting to databases, and communicating between servers and clients.

@@

\subsection{Utilisation}

Currently, we know of two frameworks implementing \TOP: \ITASKS and \MTASKS.

\ITASKS is an implementation of \TOP, in the form of a shallowly embedded domain-specific language in the lazy functional programming language Clean.
It is a library that provides editors, monadic combinators, and shared data sources.
\ITASKS uses the generic programming facilities of Clean to derive rich client and server applications from a single source.
It has been used to model an incident management tool for the Dutch coast guard~\cite{conf/iscram/LijnseJP12}.
Also it has been used numerous times to prototype ideas for Command and Control~\cite{theses/nlda/Kool17, theses/radboud/Stutterheim17}, and in a case study for the Dutch tax authority~\cite{conf/sfp/StutterheimAP17}.

@@

\subsection{Challenges}

@@

\subsection{Contributions}

@@

\begin{itemize}
  \item
    We describe the essential concepts of task-oriented programming.

  \item
    We present a formal calculus for modelling declarative workflows, embedded in a simply typed lambda-calculus, called \TOPHAT.
    It is based on the aforementioned essential \TOP concepts.

  \item
    We develop a layered operational semantics for \TOPHAT that is driven by user input.
    The semantics of the task language is clearly separated from the semantics of the underlying host language.

  \item
    Along with this semantics, we present the following semantic observations on tasks:
    the current value, whether a term is stuck, the current user interface, and the accepted inputs.

  \item
    We prove progress and type preservation for \TOPHAT.

  \item
    Using both the essential concepts and the formal calculus, we compare \TOP with related work in areas ranging from business process modelling, to process algebras and reactive programming.

  \item
    We implemented the whole semantic system in the dependently typed programming language Idris \cite{journals/jfp/Brady13}.

  \item
    To create executable applications, we implemented the task layer of \TOPHAT in iTasks.
    This also demonstrates that the former is a subset of the latter.

\end{itemize}

\subsection{Structure}

>>>>

\paragraph{Tasks}

@@

\paragraph{Task-oriented programming}
\label{sec:top}

@@

% Task-Oriented Programming (\TOP) is a programming paradigm aimed at writing interactive multi-user applications in a declarative way \cite{conf/ppdp/PlasmeijerLMAK12}.
Task-oriented programming (\TOP) is a programming paradigm which targets the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting these workflows \cite{conf/ppdp/PlasmeijerLMAK12}.
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
\TOP focusses on modelling collaboration patterns.
This gives rise to a user's need to interact and share information.
Next to that, \TOP automatically provides solutions to common development jobs like designing \GUI{s}, connecting to databases, and servers-client communication.

@@

\paragraph{Utilisation}

Currently, we know of two frameworks implementing \TOP: \ITASKS and \MTASKS.
%
\ITASKS is an implementation of \TOP, in the form of a shallowly embedded domain-specific language in the lazy functional programming language Clean.
It is a library that provides editors, monadic combinators, and shared data sources.
\ITASKS uses the generic programming facilities of Clean to derive rich client and server applications from a single source.
It has been used to model an incident management tool for the Dutch coast guard~\cite{conf/iscram/LijnseJP12}.
Also it has been used numerous times to prototype ideas for Command and Control~\cite{theses/nlda/Kool17, theses/radboud/Stutterheim17}, and in a case study for the Dutch tax authority~\cite{conf/sfp/StutterheimAP17}.

@@

\paragraph{Challenges}

@@

\paragraph{Contributions}

@@

\begin{enumerate*}
  \item
    We describe the essential concepts of task-oriented programming.
  \item
    We present a formal calculus for modelling declarative workflows, embedded in a simply typed lambda-calculus, called \TOPHAT.
    It is based on the aforementioned essential \TOP concepts.
  \item
    We develop a layered operational semantics for \TOPHAT that is driven by user input.
    The semantics of the task language is clearly separated from the semantics of the underlying host language.
  \item
    Along with this semantics, we present the following semantic observations on tasks:
    the current value, whether a term is stuck, the current user interface, and the accepted inputs.
  \item
    We prove progress and type preservation for \TOPHAT.
  \item
    Using both the essential concepts and the formal calculus, we compare \TOP with related work in areas ranging from business process modelling, to process algebras and reactive programming.
  \item
    We implemented the whole semantic system in the dependently typed programming language Idris \cite{journals/jfp/Brady13}.
  \item
    To create executable applications, we implemented the task layer of \TOPHAT in iTasks.
    This also demonstrates that the former is a subset of the latter.
\end{enumerate*}

\paragraph{Structure}
